What is a Selection Coefficient?

### 2021-10-13 graphs_newt_snakes/What_is_sel_coef.Rmd
I wrote down the things I would like to do to test beta in the what is a sel coef markdown. and I am setting up to run the 10,000 gen space simulation so I was checking to make sure it runs
setting up the beta test

>>>>

What I would like to do:

-run a simulation where newts have an advantage (run msprime with under 5 var and under 2 var)
-turn off mutations for newts
-see if snake beta goes up <-prediction
-watch newt beta <- I think it might stay around 0
-print beta every generation 
-compare space to no space

(pairs)
sigma_u2=( 0.1 0.2 0.3)
mu_rate_u2=( 1e-10 2.5e-11 1.11e-11)
sigma_u5=( 0.1 0.2 0.3)
mu_rate_u5=( 6.25e-10 1.56e-10 6.94e-11)

I made 6 msprime files where one species phenotype is under 2 and one is under 5. I kept the under 2 params the same and moved the under 5 to each of the three pairs.
